---
title: "MUSSER-GRACE-ADA-HOMEWORK-04"
author: "Grace Musser"
date: "4/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(curl)
library(readr)
library(boot)
library(simpleboot)
```

[1] Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β
 coeffiecients (slope and intercept).

```{r}
#First, read in the Kamilar and Cooper dataset:
f <- curl("https://raw.githubusercontent.com/difiore/ADA-2019/master/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = TRUE)
head(d)
```

```{r}
#Create a linear regression model for log (HomeRange_km2) in relation to log(Body_mass_female_mean)
m<-lm(log(d$HomeRange_km2) ~ log(d$Body_mass_female_mean))
m
summary(m) #report coefficients
```

```{r}
confint(m) #get confidence intervals for the model
```


[2] Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the appropriate coefficients. This generates a sampling distribution for each β
 coefficient. Plot a histogram of these sampling distributions.
 

```{r}
n <- length(d[,1]) #make sure that n matches the length of the dataset
t <- 1000 #sample times
boots <- d[sample(nrow(d), n, replace = TRUE), ] #create bootstrap with replacement
str(boots)
b0 <- rep(0,t) #beta0 values vector
b1 <- rep(0,t) #beta1 values vector

for (i in 1:t){
  boots <- d[sample(nrow(d), n, replace = TRUE), ] #boottrap with replacement
  m <- lm(data = boots, formula = log(HomeRange_km2) ~ log(Body_mass_female_mean)) #define model
  b0[i] <- m$coefficients[1] #add model coefficients to vectors
  b1[i] <- m$coefficients[2] 
  }


head(b1)
head(b0)
par(mfrow = c(1,2)) #plot histogram
hist(b0, breaks = 20)
hist(b1, breaks = 20)
par(mfrow = c(1,1))
```

[3] Estimate the standard error for each of your β
 coefficients as the standard deviation of the sampling distribution from your bootstrap.

```{r}
SEb0 <- sd(b0) #get standard error for beta coefficients
SEb0
SEb1 <- sd(b1)
SEb1
```


[4] Also determine the 95% CI for each of your β
 coefficients based on the appropriate quantiles from your sampling distribution.
 
```{r}
b0_CI_upper <- mean(b0) + qnorm(0.975) * SEb0 #get confidence errors based on quantiles using means of betas
b0_CI_lower <- mean(b0) - qnorm(0.975) * SEb0
b0_CI_upper
b0_CI_lower
b1_CI_upper <- mean(b1) + qnorm(0.975) * SEb1
b1_CI_lower <- mean(b1) - qnorm(0.975) * SEb1
b1_CI_lower
b1_CI_upper
```

[5] How does your answer to part [3] compare to the SE estimated from your entire dataset using the formula  for standard error implemented in lm()?

The original estimates were 0.67293 and 0.08488, whereas those estimated from the bootstrap were 0.6120576 and 0.07923245. The bootstrap standard errors were similar but slightly lower than the original estimates.

[6] How does your answer to part [4] compare to the 95% CI estimated from your entire dataset?

The original confidence interval estimates -10.7720889 to -8.110374 and 0.8685707 to 1.204292, whereas the bootstrap estimates were -10.66909 to -8.26987 and 0.8839389 to 1.194524. Thus they are nearly identical.

EXTRA CREDIT: + 2

Write a FUNCTION that takes as its arguments a dataframe (“d”), a linear model (“m”, as a character string, e.g., “logHR~logBM”), a user-defined confidence interval level (“conf.level”) with default = 0.95, and a number of bootstrap replicates (“n”, with default = 1000). Your function should return a dataframe that includes: beta coefficient names; beta coefficients, standard errors, and upper and lower CI limits for the linear model based on your entire dataset; and mean beta coefficient estimates, SEs, and CI limits for those coefficients based on your bootstrap.


```{r}

f<-function(d, m, conf.level=0.95, t=1000){
  m<-lm(log(d$HomeRange_km2) ~ log(d$Body_mass_female_mean))
  s<-summary(m)
  ci<-confint(m)
  dsample <- d[sample(nrow(d), n, replace = T), ]
  head(dsample)
  str(dsample)
  n <- length(d[,1]) #make sure that n matches the length of the dataset
  boots <- d[sample(nrow(d), n, replace = TRUE), ] #create bootstrap with replacement
  str(boots)
  b0 <- rep(0,t) #beta0 values vector
  b1 <- rep(0,t) #beta1 values vector
  for (i in 1:t){
    boots <- d[sample(nrow(d), n, replace = TRUE), ] #boottrap with replacement
    m <- lm(data = boots, formula = log(HomeRange_km2) ~ log(Body_mass_female_mean)) #define model
    b0[i] <- m$coefficients[1] #add model coefficients to vectors
    b1[i] <- m$coefficients[2] 
    }
  SEb0 <- sd(b0) #get standard error for beta coefficients
  SEb0
  SEb1 <- sd(b1)
  SEb1
  b0_CI_upper <- mean(b0) + qnorm(0.975) * SEb0 #get confidence errors based on quantiles using means of betas
  b0_CI_lower <- mean(b0) - qnorm(0.975) * SEb0
  b0CI<-c(b0_CI_upper, b0_CI_lower)
  b1_CI_upper <- mean(b1) + qnorm(0.975) * SEb1
  b1_CI_lower <- mean(b1) - qnorm(0.975) * SEb1
  b0CI<-c(b1_CI_lower, b1_CI_upper)
  print(s)
  print(ci)
  print(b0CI, b0CI)
  print(SEb0)
  print(SEb1)
  }


```

```{r}
f(d, m, conf.level, n)
```


